\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

% CV Info (to be customized).
\newcommand{\CVAuthor}{Mauri Mustonen}
\newcommand{\CVTitle}{Mauri Mustonen CV}
%\newcommand{\CVNote}{CV compiled on {\today} for Acme Corporation}
\newcommand{\CVWebpage}{https://mauri.codes}

% PDF settings and properties.
\hypersetup{pdftitle={\CVTitle},
    pdfauthor={\CVAuthor},
    pdfsubject={\CVWebpage},
    pdfcreator={XeLaTeX},
    pdfproducer={},
    pdfkeywords={},
    unicode=true,
    bookmarks=true,
    bookmarksopen=true,
    pdfstartview=FitH,
    pdfpagelayout=OneColumn,
    pdfpagemode=UseOutlines,
    hidelinks,
    breaklinks
}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

\begin{document}

% Title

\Title{\CVAuthor}

\begin{SubTitle}
    \par
    \href{mailto:mauri\_mustonen@hotmail.com}{mauri\_mustonen@hotmail.com}\,
    \SubBulletSymbol\,
    \href{https://github.com/kazhuu}{https://github.com/kazhuu}\,
    \SubBulletSymbol\,
    \href{\CVWebpage}{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

% Education

\Section{Education}{Education}{PDF:Education}

\Entry
\textbf{Tampere University of Technology}, Tampere, Finland
\hfill
\DatestampYMD{2016}{5}{} -- \DatestampYMD{2018}{12}{}
\Gap
\BulletItem
M.Sc. in Software Engineering with Distinction
\begin{Detail}
    \SubBulletItem Cumulative GPA: 4.52 / 5.0
\end{Detail}

\BigGap
\Entry
\textbf{Karelia University of Applied Sciences}, Joensuu, Finland
\hfill
\DatestampYMD{2012}{05}{} -- \DatestampYMD{2016}{05}{}
\Gap
\BulletItem
Information Engineer in Software
\begin{Detail}
    \SubBulletItem Cumulative GPA: 4.50 / 5.00
\end{Detail}

\BigGap
\Entry
\textbf{Vocational School Avartum Oy}, Joensuu, Finland
\hfill
\DatestampYMD{2010}{05}{} -- \DatestampYMD{2019}{05}{}
\Gap
\BulletItem
Vocational Qualification in Business and Administration

\BigGap
\Entry
\textbf{Vocational School Peltola}, Joensuu, Finland
\hfill
\DatestampYMD{2004}{05}{} -- \DatestampYMD{2007}{05}{}
\Gap
\BulletItem
Electronics Technician

% Experience

\Section{Experience}{Experience}{PDF:Experience}

\Entry
\textbf{Wapice Oy}, Tampere, Finland
\hfill
\DatestampY{2019} -- Present
\Gap
\begin{Details}
    \SubBulletItem Embedded Software Developer
    \SubBulletItem Embedded development with C and C++ up to C++17
    \SubBulletItem Real time OS, ARMv7 architecture and driver development
    \SubItem for custom harware blocks.
\end{Details}

\BigGap
\Entry
\textbf{Alsus Oy}, Tampere, Finland
\hfill
\DatestampY{2017} -- \DatestampY{2019}
\Gap
\BulletItem Full Stack Web Developer
\begin{Details}
    \SubBulletItem Web development (e.g Ruby on Rails, AngularJS).
    \SubBulletItem Distributed system architect and developer (e.g. Linux, C, Ruby, \\
    CMake, AMQP, Redis)
    \SubBulletItem Writing Ruby native extensions to C language
    \SubBulletItem Contributing to open source (e.g. Ruby on Rails, libIEC6850)
\end{Details}


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Other Work\newline
Experience}
{Other Work Experience}
{PDF:OtherWorkExperience}

\Entry
\href{http://www.example.com/my-company}
{\textbf{Alpha Engineering Firm}},
Oakland, Ohio, USA

\Gap
\BulletItem
Project Officer,
Department of Meteorological Sciences,
\hfill
\DatestampYMD{2007}{10}{15} --
\DatestampYMD{2008}{01}{15}
\newline
Research \& Development Division
\begin{Detail}
    \SubBulletItem
    Nullam venenatis egestas nisl eget elementum.
    \SubBulletItem
    Nulla finibus justo vel turpis efficitur, non lacinia orci maximus. Proin rhoncus, felis vel hendrerit lacinia, enim ipsum ultricies massa, sit amet interdum nisi massa sit amet justo.
    \SubBulletItem
    Etiam vitae eros mollis, consectetur quam quis, molestie massa.
\end{Detail}

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\Section
{Languages}
{Languages}
{PDF:Languages}

\BulletItem
English: Native language.

\Gap
\BulletItem
Spanish: Fluent (speaking, reading, writing).

\Gap
\BulletItem
Latin: Intermediate (reading); basic (speaking, writing).

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\Entry
{\TeX}, {\LaTeX}, {\XeLaTeX},
MATLAB,
Mathematica,
Maple,
R,
Tableau,
Adobe Photoshop,
Adobe Illustrator,
Microsoft Word,
Microsoft Excel,
Microsoft PowerPoint.

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\Section
{Interests}
{Interests}
{PDF:Interests}

\Entry
Digital photography,
typography,
swimming.

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

\Section
{References}
{References}
{PDF:References}

\BulletItem
\textbf{Professor Jonathan Public}
\newline
Professor of Geology and Mechanical Engineering
\newline
First American University
\newline
1000 First Avenue, Springfield, Massachusetts 22222, USA
\newline
\href{mailto:jonathanpublic@example.com}
{jonathanpublic@example.com}
\,\SubBulletSymbol\,
+1\,(555)\,222-2222

\BigGap
\BulletItem
\textbf{Dr Alice Bob Carol}
\newline
Director, Research \& Development
\newline
Alpha Engineering Firm
\newline
20 North Street, Oakland, Ohio 33333, USA
\newline
\href{mailto:alicebobcarol@example.com}
{alicebobcarol@example.com}
\,\SubBulletSymbol\,
+1\,(555)\,333-3333

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MULTILINGUAL UNICODE EXAMPLES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Multilingual Unicode Examples}
{Multilingual Unicode Examples}
{PDF:MultilingualUnicodeExamples}

\BulletItem
Assortment of unicode characters from
\href{http://www.ltg.ed.ac.uk/~richard/unicode-sample.html}
{\url{http://www.ltg.ed.ac.uk/~richard/unicode-sample.html}}

\begin{Detail}
    \Item
    \textbf{Latin Extended-A}
    Ā ā Ă ă Ą ą Ć ć Ĉ ĉ Ċ ċ Č č Ď ď Đ đ Ē ē Ĕ ĕ Ė ė Ę ę Ě ě Ĝ ĝ Ğ ğ Ġ ġ Ģ ģ Ĥ ĥ Ħ ħ Ĩ ĩ Ī ī Ĭ ĭ Į į İ ı Ĳ ĳ Ĵ ĵ
    \textbf{Latin Extended-B}
    ƀ Ɓ Ƃ ƃ Ƅ ƅ Ɔ Ƈ ƈ Ɖ Ɗ Ƌ ƌ ƍ Ǝ Ə Ɛ Ƒ ƒ Ɠ Ɣ ƕ Ɩ Ɨ Ƙ ƙ ƚ ƛ Ɯ Ɲ ƞ Ɵ Ơ ơ Ƣ ƣ Ƥ ƥ Ʀ Ƨ ƨ Ʃ ƪ ƫ Ƭ ƭ Ʈ Ư ư Ʊ Ʋ Ƴ ƴ Ƶ
    \textbf{Latin Extended Additional}
    Ḁ ḁ Ḃ ḃ Ḅ ḅ Ḇ ḇ Ḉ ḉ Ḋ ḋ Ḍ ḍ Ḏ ḏ Ḑ ḑ Ḓ ḓ Ḕ ḕ Ḗ ḗ Ḙ ḙ Ḛ ḛ Ḝ ḝ Ḟ ḟ Ḡ ḡ Ḣ ḣ Ḥ ḥ Ḧ ḧ Ḩ ḩ Ḫ ḫ Ḭ ḭ Ḯ ḯ Ḱ ḱ Ḳ ḳ Ḵ ḵ
    \textbf{Greek}
    ʹ ͵ ͺ ; ΄ ΅ Ά · Έ Ή Ί Ό Ύ Ώ ΐ Α Β Γ Δ Ε Ζ Η Θ Ι Κ Λ Μ Ν Ξ Ο Π Ρ Σ Τ Υ Φ Χ Ψ Ω Ϊ Ϋ ά έ ή ί ΰ α β γ δ ε ζ η θ
    \textbf{Cyrillic}
    Ё Ђ Ѓ Є Ѕ І Ї Ј Љ Њ Ћ Ќ Ў Џ А Б В Г Д Е Ж З И Й К Л М Н О П Р С Т У Ф Х Ц Ч Ш Щ Ъ Ы Ь Э Ю Я а б в г д е ж з
    \textbf{Hebrew}
    א ב ג ד ה ו ז ח ט י ך כ ל ם מ ן נ ס ע ף פ ץ צ ק ר ש ת װ ױ ײ ֝ ֞ ֟ ֠ ֡ ֣ ֤ ֥ ֦ ֧ ֨ ֩ ֪ ֫ ֬ ֭ ֮ ֯ ְ ֱ ֒ ֓ ֔
    \textbf{Armenian}
    {\UseSecondaryFont
    Ա Բ Գ Դ Ե Զ Է Ը Թ Ժ Ի Լ Խ Ծ Կ Հ Ձ Ղ Ճ Մ Յ Ն Շ Ո Չ Պ Ջ Ռ Ս Վ Տ Ր Ց Ւ Փ Ք Օ Ֆ ՙ ՚ ՛ ՜ ՝ ՞ ՟ ա բ գ դ ե զ}
    \textbf{Thai}
    {\UseSecondaryFont
    ก ข ฃ ค ฅ ฆ ง จ ฉ ช ซ ฌ ญ ฎ ฏ ฐ ฑ ฒ ณ ด ต ถ ท ธ น บ ป ผ ฝ พ ฟ ภ ม ย ร ฤ ล ฦ ว ศ ษ ส ห ฬ อ ฮ ฯ ะ ั า ำ ิ}
\end{Detail}

% Manual page break.
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% THIS IS A SECTION WITH USAGE NOTES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Declare a new group to limit the scope of \color to this section.
\begingroup
\color{blue}

\Section
{This is a\newline
Section\newline
With\newline
Usage Notes}
{This is a Section With Usage Notes (For PDF Bookmark)}
{PDF:ThisIsASectionWithUsageNotes:ForPDFLink}

\SubSection
{This is a SubSection}
{This is a SubSection (For PDF Bookmark)}
{PDF:ThisIsASubSection:ForPDFLink}

\BigGap
\BulletItem
Use \CodeCommand{Section\{a\}\{b\}\{c\}} and
\CodeCommand{SubSection\{a\}\{b\}\{c\}}
to create sections and subsections, where
\Code{a} is the heading displayed on the page,
\Code{b} is the PDF bookmark heading, and
\Code{c} is the internal PDF link (must be unique).
Sections and subsections will appear in the PDF bookmarks.
Note the CamelCase command names.

\Gap
\BulletItem
Use
\CodeCommand{Entry},
\CodeCommand{BulletItem},
\CodeCommand{SubBulletItem},
\CodeCommand{SubSubBulletItem},
\CodeCommand{Item},
\CodeCommand{SubItem},
\CodeCommand{SubSubItem},
\CodeCommand{NumberedItem},
etc.,
to create entries in the main body of the CV.

\Gap
\BulletItem
Enclose entry details between
\CodeCommand{begin\{Detail\}} and
\CodeCommand{end\{Detail\}}
so that they are typeset in a smaller font.
\begin{Detail}
    \Item
    This is an example of entry detail text enclosed in a \Code{Detail} environment.
\end{Detail}

\Gap
\BulletItem
Use \CodeCommand{Gap} and \CodeCommand{BigGap} to insert vertical spaces between entries to improve layout.

\BigGap
\SubSection
{This is Another SubSection}
{This is Another Subsection (For PDF Bookmark)}
{PDF:ThisIsAnotherSubSection:ForPDFLink}

\BigGap
\Entry
This is a plain \CodeCommand{Entry},
followed by an \CodeCommand{hfill} and a date range
\hfill
\DatestampYM{2015}{10} --
\DatestampYM{2015}{12}

\Gap
\BulletItem
This is a \CodeCommand{BulletItem}.
\Item
This is an \CodeCommand{Item}, which has no bullet.
Note the alignment with the \CodeCommand{BulletItem} above.

\Gap
\SubBulletItem
This is a \CodeCommand{SubBulletItem}.
\SubItem
This is a \CodeCommand{SubItem}, which has no bullet.
Note the alignment with the \CodeCommand{SubBulletItem} above.

\Gap
\SubSubBulletItem
This is a \CodeCommand{SubSubBulletItem}.
\SubSubItem
This is a \CodeCommand{SubSubItem}, which has no bullet.
Note the alignment with the \CodeCommand{SubSubBulletItem} above.

\Gap
\NumberedItem{[42]}
This is a \CodeCommand{NumberedItem}.
Change the value of the macro \CodeCommand{MaxNumberedItem} to adjust the indentation width.

\BigGap
\SubSection
{Line, Paragraph, and Page Breaks}
{Line, Paragraph, and Page Breaks (For PDF Bookmark)}
{PDF:LineParagraphAndPageBreaks:ForPDFLink}

\BigGap
\BulletItem
To create a new line within the same paragraph (i.e., preserving the same paragraph indentation), use \CodeCommand{newline} instead of \CodeCommand{\textbackslash};
the latter will reset the paragraph indentation.

\Gap
\BulletItem
To create a new paragraph, use \CodeCommand{par} or simply leave an empty line.
Paragraph indentations (from
\CodeCommand{Entry},
\CodeCommand{BulletItem},
\CodeCommand{SubBulletItem},
\CodeCommand{SubSubBulletItem},
\CodeCommand{Item},
\CodeCommand{SubItem},
\CodeCommand{SubSubItem},
\CodeCommand{NumberedItem},
etc.) do not carry across different paragraphs.

\Gap
\BulletItem
To create a new page, use \CodeCommand{newpage}.

\BigGap
\SubSection
{Dates}
{Dates (For PDF Bookmark)}
{PDF:Dates:ForPDFLink}

\BigGap
\BulletItem
Use the following macros to specify and display dates consistently:
\SubBulletItem
\CodeCommand{DatestampYMD\{yyyy\}\{MM\}\{dd\}}
(e.g., \CodeCommand{DatestampYMD\{2008\}\{01\}\{15\}})
\SubBulletItem
\CodeCommand{DatestampYM\{yyyy\}\{MM\}}
(e.g., \CodeCommand{DatestampYM\{2008\}\{01\}})
\SubBulletItem
\CodeCommand{DatestampY\{yyyy\}}
(e.g., \CodeCommand{DatestampY\{2008\}})

\Gap
\BulletItem
Change the date format option passed to the document class to adjust how dates are displayed throughout the document:
\SubBulletItem
\Code{MMMyyyy} (``Jan~2008'')
\SubBulletItem
\Code{ddMMMyyyy} (``15~Jan~2008'')
\SubBulletItem
\Code{MMMMyyyy} (``January~2008'')
\SubBulletItem
\Code{ddMMMMyyyy} (``15~January~2008'')
\SubBulletItem
\Code{yyyyMMdd} (``2008-01-15'')
\SubBulletItem
\Code{yyyyMM} (``2008-01'')
\SubBulletItem
\Code{yyyy} (``2008'')

\endgroup

\end{Body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\BigGap
\UseNoteFont%
\null\hfill%
%[\textit{\CVNote}]

\end{document}
